The Sub-Millimetre User Reduction Facility: an iterative map-maker for SCUBA-2

### 2010-11-25 smurf_paper.tex
SMO can be mean or median
more outline stuff + added stompor reference

@@

Describe the bolometer signal model, and with the help of a flow-chart
show the basic procedure that SMURF follows.

@@

\begin{figure}
\centering
\includegraphics[width=0.75\linewidth]{dimm.pdf}
\caption{Typical map-making algorithm. Raw data (stored in multiple
  files) are read and concatenated into continuous time series. A
  pre-processing stage repairs DC steps, applies a flatfield
  correction, identifies and removes the noisiest bolometers, and
  flags large spikes. The iterative portion then begins: estimating
  and removing the common-mode signal; applying the extinction
  correction; high-pass filtering to remove residual independent
  low-frequency noise; estimating the map by re-gridding the data; and
  finally measuring the noise in the residual time series. If the
  \rms\ has converged, the final map is written to disk. Otherwise any
  multiplicative factors that may have been applied to the data are
  inverted (e.g., extinction correction and relative gains measured
  during the common-mode calculation), and each additive component is
  added back into the time series and re-estimated in turn.}
\label{fig:dimm}
\end{figure}

@@

We also have the SMO median filter that's useful for very short scans
because edge effects don't matter so much.

@@

Discuss gap filling, ``new'' window function method, also apodization
and start/end polynomial continuity stuff. Should reference CMB
literature (namely Stompor et al.).

>>>>

\subsubsection{Scan strategy}

@@

\begin{itemize}

\item Describe the bolometer signal model, and with the help of a flow-chart
show the basic procedure that SMURF follows.

\item Discuss SMURF configurability

\item Some sort of proof/demonstration showing why the algorithm works

\item Discuss performance (execution time, memory, disk usage etc.)

\item Where do you get SMURF/starlink, usage of NDF

\item Talk about pipeline?

\end{itemize}

@@

\begin{figure}
\centering
\includegraphics[width=0.75\linewidth]{dimm.pdf}
\caption{Typical map-making algorithm. Raw data (stored in multiple
  files) are read and concatenated into continuous time series. A
  pre-processing stage repairs DC steps, applies a flatfield
  correction, and identifies and removes the noisiest bolometers. The
  iterative portion then begins: estimating and removing the
  common-mode signal; applying the extinction correction; high-pass
  filtering to remove residual independent low-frequency noise;
  estimating the map by re-gridding the data; and finally measuring
  the noise in the residual time series. If the \rms\ has converged,
  the final map is written to disk. Otherwise any multiplicative
  factors that may have been applied to the data are inverted (e.g.,
  extinction correction and relative gains measured during the
  common-mode calculation), and each additive component is added back
  into the time series and re-estimated in turn.}
\label{fig:dimm}
\end{figure}

@@

We also have the SMO filter that's useful for very short scans
because edge effects don't matter so much. Two sorts - median which is
more robust, or mean which is more accurate.

@@

Discuss gap filling, ``new'' window function method, also apodization
and start/end polynomial continuity stuff. Should reference CMB
literature -- in particular look at \citet{stompor2002}.
